A Meta-Analysis of Music Emotion Recognition Studies

### 2025-03-10 manuscript/manuscript-apaquarto.qmd
Added a template for compiling a pdf version of MS using apaquarto, removed flextable

```{r}
#| label: tbl-table1
#| tbl-cap: Summary of the models for regression and classification studies.
#| ft.align: left
#| warning: false
#| message: false

library(tidyverse)
library(flextable)

tibble(Info = c("Study N","Model N","Techniques","Techniques","Techniques","Techniques","Techniques","Feature N","Stimulus N"), 
       Regression = c("22","204","Neural Nets: 64","Support Vector Machines: 62","Linear Methods: 62","Tree-based Methods: 14","KS, Add. & KNN: 2","Min=3, Md=653, Max=14460","Min=20, Md=324, Max=2486"),
       Classification = c("12","86","21","26","19","16","4","Min=6, Md=98, Max=8904","Min=124, Md=300, Max=5192"),
       Total = c("34","290","85","88","81","30","6","NA","NA")) %>% 
  flextable(cwidth = c(.7,2.3,2.3,.4)) %>%
  theme_apa() 
```

>>>>

```{r}
#| label: tbl-table1
#| id: tbl-table1
#| output: asis
#| warning: false
#| message: false
#| tbl-cap: Summary of the models for regression and classification studies.
library(tidyverse)
library(kableExtra)

t <- tibble(Info = c("Study N","Model N","Techniques","Techniques","Techniques","Techniques","Techniques","Feature N","Stimulus N"), 
       Regression = c("22","204","Neural Nets: 64","Support Vector Machines: 62","Linear Methods: 62","Tree-based Methods: 14","KS, Add. & KNN: 2","Min=3, Md=653, Max=14460","Min=20, Md=324, Max=2486"),
       Classification = c("12","86","21","26","19","16","4","Min=6, Md=98, Max=8904","Min=124, Md=300, Max=5192"),
       Total = c("34","290","85","88","81","30","6","NA","NA")) 
print(knitr::kable(t,bookstabs=TRUE))
#  theme_apa()
